\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
Polishing conclusion

The task that we have presented was initially motivated by those two questions:

\begin{enumerate}
    \item Can we characterise the participants' behaviours that
        lead to good performance during the interaction? In particular, do
        we observe any anticipation patterns for the good performers?

    \item How does visual cue affects the performance of the participants?

@@

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do
participants look when they want to understand a robot behaviour? Does
\emph{anticipation} reflect understanding? How the robot's design impact the
interaction?

We believe that mobile eye-tracking, as a relatively non-invasive yet accurate
(both spatially and temporally) biometric measurement, is a key tool to
investigate this kind of questions in ecologically valid environments.

In that regard, we identify three main strengths of eye-tracking. First,
eye-tracking introduce less experimental bias: mobile eye-tracker are
non-invasive and lightweight. Combined with mobile recording units, they do not
put any constraints on participant movements, contrary to traditional techniques
like video recording. Also, contrary to questionnaires or interview-based
protocol where the experimenter active role may influence the assessment,
eye-tracker are easy to ``forget about'' for the participants.

Second, eye-tracking provides a direct, un-mediated access to the subject's
attentional focus~\cite{sharma2014withmeness} (both spatially -- where does the
subject look at -- and temporally -- where does the subject's attention stays).
Importantly, this information leads to a fine-grained measure of
\emph{engagement}.  Also, the good temporal resolution of eye-trackers allows
for the accurate study of the \emph{dynamics} of attention: what are the
attentional patterns of the subject during the interaction.

Third, it has been showed in literature that eye-tracking can provide an
effective measure of higher socio-cognitive behaviours: it can be used as a
predictor for successful joint task achievement~\cite{sharma2013understanding},
or as a measure of \emph{interaction quality}~\cite{jermann2012effects} through
measurement of joint attention.

@@

Besides, mobile eye-tracking come with an additional cost. As
we mentioned earlier, the automatic localisation of the gaze pointer on
the visual stimulus is not a trivial task. In our study, we relied on a 
number of fiducial markers to the playground, but they were reported as
distractive by the participants. More complex computer vision tools (object
tracking) can alleviate the need for such markers, but it certainly requires
significant pre-processing prior to data analysis.

>>>>

The robotic task that we have just presented was initially motivated by those
two questions:

\begin{enumerate}
    \item Can we \emph{characterise} the participants' behaviours that
        lead to good performance during the interaction? In particular, do
        we observe any higher cognitive skills like anticipation patterns for
        the good performers?

    \item How do visual cues affect the performance of the participants?

@@

We indeed were interested in accessing and understanding the cognitive
mechanisms at stake during the interaction: where do participants look when they
want to understand a robot behaviour? Does \emph{anticipation} for instance
reflect understanding? How the robot's design impact the interaction? These kind
of questions are common in HRI, and ee believe that mobile eye-tracking, as a
relatively non-invasive yet accurate (both spatially and temporally) biometric
measurement, is a valuable tool to investigate them in ecologically
valid environments.

We identify three main strengths of eye-tracking. First, eye-tracking introduces
less experimental bias: mobile eye-tracker are non-invasive and lightweight.
Combined with mobile recording units, they do not put any constraints on
participant movements, contrary to traditional techniques like video recording.
Also, contrary to questionnaires or interview-based protocols where the
experimenter's active role may influence the participants' answers, eye-trackers
are easy to ``forget about'' for the participants.

Second, eye-tracking provides a direct, un-mediated access to the subject's
attentional focus~\cite{sharma2014withmeness} (both spatially -- where does the
subject look at -- and temporally -- where does the subject's attention remain).
Importantly, this information can be implicitly interpreted as a fine-grained measure of
\emph{engagement}.  Also, the good temporal resolution of eye-trackers allows
for the accurate study of the \emph{dynamics} of attention, including possible
\emph{attentional patterns} of the subject during the interaction.

Third, it has been shown in literature that eye-tracking can provide an
effective measure of higher socio-cognitive behaviours: it can be used as a
predictor for successful joint task achievement~\cite{sharma2013understanding},
or as a measure of \emph{interaction quality}~\cite{jermann2012effects} through
measurement of joint attention.

@@

Besides, mobile eye-tracking come with an additional cost. As we mentioned
earlier, the automatic localisation of the gaze pointer on the visual stimulus
is not a trivial task. In our study, we relied on a number of fiducial markers
to the playground, but they were reported as distractive by the participants.
More complex computer vision tools (like object tracking) can alleviate the need
for such markers, but it certainly requires significant pre-processing prior to
data analysis.
